State of the Practice for Medical Imaging Software

### 2022-10-12 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Edits to SOP for MI, mainly section 9 (pain points), some parts removed from Section 10 (recommendations)

We based uur interviews on a list of 20 questions, which can be found in
\citet{SmithEtAl2021}. Some questions are about the background of the software,
the development teams, the interviewees, and how they organize the projects. We
also ask about the developer's understandings of the users. Some questions focus
on the current and past difficulties, and the solutions the team has found, or
will try. We also discuss the importance and current situations of
documentation. A few questions are about specific software qualities, such as
maintainability, understandability, usability, and reproducibility. The
interviews are semi-structured based on the question list; we ask follow-up
questions when necessary.  The interview process presented here was approved by
the McMaster University Research Ethics Board under the application number 
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/MACREM/Application.pdf}
{MREB\#: 5219}.

@@

We identified the use of unit testing in less than half of the 29 projects. On
the other hand, the interviewees believed that testing (including usability
tests with users) was the top solution to improve correctness, usability, and
reproducibility.  This level of testing matches what was observed for LBM
software \citep{Michalski2021} and is apparently greater than the level of
testing for ocean modelling software.  \citet{JungEtAl2022} reports that testing
is underemphasized in ocean modelling.

As the observed artifacts in Table~\ref{artifactspresent} show, documentation is
not emphasized as part of the development process in any of the 29 projects.
None of them had theory manuals, although we did identify a road map in the
\textit{3D Slicer} project.  No requirements specifications were found.
Table~\ref{tab_opinion_doc} summarizes interviewees' opinions on documentation.
Interviewees from each of the eight projects thought that documentation was
essential to their projects, and most of them said that it could save their time
to answer questions from users and developers. Most of them saw the need to
improve their documentation, and only three of them thought that their
documentations conveyed information clearly enough. Nearly half of developers
also believed that the lack of time prevented them from improving documentation.

@@

As Table~\ref{Tbl_Guidelines} suggests, an emphasis on documentation, especially
for new developers, is echoed in research software guidelines. Multiple
guidelines recommend a document explaining how to contribute to a project, often
named CONTRIBUTING. Guidelins also recommend tutorials, user guides and quick start examples. \citet{SmithAndRoscoe2018} suggests including instructions
specifically for on-boarding new developers. For open source software in general
(not just research software), \citet{Fogel2005} recommends providing tutorial
style examples, developer guidelines, demos, and screenshots.

@@

Our interviews identified pain points related to lack of time and funding,
technology hurdles, improving correctness, and improving usability.  In this
section, we go through each pain point and contrast the MI experience with
observations from other domains.  We also cover potential ways to address the
pain points, as promoted by the community.  (Later, in
Section~\ref{ch_recommendations}, we propose additional pain mitigation
strategies based on our experience.)  In addition to pain points, we summarize
MI developer strategies for improving maintainability and reproducibility.
Although these two qualities were not explicitly idenfied as pain points, they
were discussed as part of our interview process \citep{SmithEtAl2021}.  The
interviewee's practices for addressing pain points and improving quality can
potentially be emulated by other MI developers. Moreover, these practices may
provide examples that can be followed by other research software domains.

[CHECK  THESE, after writing all the PPs] \citet{PintoEtAl2018} lists some pain
points that did not come up in our conversations with MI developers :
Cross-platform compatibility, interruptions while coding, scope bloat, lack of
user feedback, hard to collaborate on software projects, and aloneness.
\citet{WieseEtAl2019} repeat some previous pain points and add the following:
dependency management, data handling concerns (like data quality, data
management and data privacy) [Actually mentioned by MI software],
reproducibility, and software scope determination. Although MI developers did
not mention these pain points, we cannot conclude that they are not relevant for
MI software development, since we only interviewed nine MI developers for about
an hour each.

@@

\begin{itemize}
\item Shifting from development to maintenance when the team does not have
enough developers for building new features and fixing bugs at the same time;
\item Improving documentation to save time answering users' and developers'
questions;
\item Supporting third-party plugins and extensions; and,
\item Using GitHub Actions for continunous integration and continuous
development.
\end{itemize}

\item[P\refstepcounter{pnum}\thepnum \label{P_LackFunding}:] \textbf{Lack of
Funding:} Developers felt the pain of having to attract funding to develop and
maintain their software. For instance, the interviewees from \textit{3D Slicer}
and \textit{OHIF} said getting funding for software maintenance is more
challenging than finding funding for research. The interviewee from the
\textit{ITK-SNAP} team thought more fundings was a way to solve the lack of time
problem, because they could hire more dedicated developers. On the other hand,
the interviewee from the \textit{Weasis} team did not feel that fundings could
solve the same problem, since he would still need time to supervise the project.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_TechnologyHurdles}:]
\textbf{Technology Hurdles:} The technology hurdles mentioned by MI developers
include: hard to keep up with changes in OS and libraries, difficult to transfer
to new technologies, hard to support multiple OS, and hard to support lower-end
computers. Developers expressed difficulty balancing between four factors:
cross-platform compatibility, convenience to development and maintenance,
performance, and security.

@@

\begin{itemize}
\item Adopting a web-based approach with backend servers, to better support
lower-end computers;
\item Using memory-mapped files to consume less computer memory, to better
support lower-end computers; 
\item Using computing power from the computers GPU for web applications;
\item Increasing funding;
\item Maintaining better documentations to ease the development and maintenance
processes;
\item Improving performance via more powerful computers, which one interviewee
pointed out has already happened to reduce the balance problem.
\end{itemize}

As the above list shows, developers perceive that web-based applications will
address the technology hurdle.  Table~\ref{tab_native_vs_web} shows the teams'
choices between native application and web application. Most of the 29 teams (24
of 29, or 83\%) chose to develop native applications. For the eight teams we
interviewed, three of them were building web applications, and the
\textit{MRIcroGL} team was considering web-based solutions.

@@

**start editing here** Change to others have trouble getting developers to test.
That isn't the problem for MI.  Testing is also a pain point for other research
software domains point. For instance, \citet{PintoEtAl2018} mention the problem
of insufficient testing and \citet{HannayEtAl2009} show that more developers
think testing is important than the number that believe they have a sufficient
understanding of testing concepts. \citet{WieseEtAl2019} mention data handling
concerns (like data quality, data management and data privacy).
\citet{HannayEtAl2009, KanewalaAndBieman2013, KellyEtAl2011, WieseEtAl2019}
point to the oracle problem, which occurs in research software when we do not
have a means to judge the correctness of the calculated solutions. For the
specific case of LBM developers, testing challenges include difficulty with
testing the correctness of large numbers of features, and challenges with
automated testing, since free testing services do not offer adequate facilities
for large amounts of data \citep{SmithEtAl2022}.

Testing was the most often mentioned strategy for MI developers for ensuring
correctness.  Seven teams mentioned test related activities, including
test-driven development, component tests, integration tests, smoke tests,
regression tests, self tests and automated tests.  Another approach frequently
adopted (mentioned by 3 interviewees) is a two state development process with
stable releases and nightly builds.  Other strategies for ensuring correctness
that came up during the interviews include CI/CD, using de-identified copies of
medical images for debugging, sending beta versions to medical workers who can
access the data to do the tests, and collecting/maintaining a dataset of
problematic images.  Some additional strategies used by MI developers include:

\begin{itemize}
\item Using open datasets
\item Asking the users to provide de-identified copies of medical images if they
have problems loading the images;
\item Sending the beta versions of software to medical workers who can access
the data and complete the tests;
\item If (part of) the team belongs to a medical school or a hospital, using the
datasets they can access;
\item If the team has access to MRI scanners, self-building sample images for
testing;
\item If the team has connections with MI equipment manufacturers, asking for
their help on data format problems;
\item Storing all images that cause special problems, and maintaining this
special dataset over time.
\end{itemize}

@@

% Hard to maintain good documentations % from Ao
% \begin{itemize}
%     \item Hard to have a high level roadmap from the start
%     \item Only a few people fully understand the large codebase
% \end{itemize}

\item[P\refstepcounter{pnum}\thepnum \label{P_Usability}:]
\textbf{Usability:} Several developers noted that users sometimes try to use
incorrect LBM method combinations to solve their problems. Furthermore, some
users think that the packages will work out of the box to solve their cases,
while in reality CFD knowledge needs to be applied to correctly modify the
packages for the new endeavour.  Some respondents in the survey of
\citet{WieseEtAl2019} also mentioned that users do not always have the expertise
required to install or use the software.

%\item Not enough participants for usability tests %from Ao
%Hard to understand users' needs % from Ao

The discussion with the developers focused on understandability issues for two
classes of users: the end users and other developers.  The threats to
understandability for end users include users not understanding how to use
features (\wss{Because the users don't have sufficient background?  Ask Ao.})
\ad{Did you mean medical or medical imaging background? No, it was majorly
caused by the software usability. Based on the context of our interview
conversations, it means that users don't understand how to complete certain
operations or what functions a feature provides. It's due to unclear
description, lack of documentation, poorly designed UI or nonintuitive process},
the team not having a dedicated user experience (UX) designer, some important
indicators are not noticeable (e.g. a progress bar), not all users understand
the purpose of the software, not all users know if the software includes certain
features, not all users understand how to use the command line tool, not all
users understand that the software is a web application. For developers the
threats to understandability include developers not understanding how to deploy
the software (\wss{This sounds like a consequence of a lack of
understandability, rather than threat to it.  Or is the point that developers
lack sufficient background?  Ask Ao}) \ad{Yes, this should be a consequence of a
lack of understandability. I think the direct cause is that the project doesn't
clearly explain how to deploy. We did not discuss the background of the
developers at that point.}, and the architecture is difficult for new developers
to understand.

The most common strategy, cited by 4 developers, for ensuring understandability
was to use documentation (user manuals, mailing lists, forums).  Other suggested
and practiced strategies include a graphical user interface, testing every
release with active users, making simple things simple and complicated things
possible, icons with clear visual expressions, designing the software to be
intuitive, having a UX designer with the right experience, dialog windows for
important notifications, and providing an example for users to follow.

The two most frequently mentioned strategies (mentioned 3 times each) for
improving usability are:
\begin{inparaenum}[i)]
    \item usability tests and interviews with end users; and,
    \item adjusting the software according to user feedback.
\end{inparaenum}
Other ideas that came up include a straightforward and intuitively designed
interface / professional UX designer, providing step-by-step processes, making
the basic functions easy to use without reading the documentation, focusing on
limited number of functions, making the software more streamlined, downsampling
images to consume less memory, and an option to load only part of the data to
boost performance.

@@

blurb to explain the ones that are coming were not explicitly identified as pain
points.

\begin{enumerate}
\item \textbf{Maintainability:} The developer of ESPResSo said that they
originally wrote their source code with a specific application in mind, which
later caused too much coupling between components in the source code. This
resulted in technical debt \citep{KruchtenEtAl2012}, which has an impact on
future maintainability and reusability. Concern with technical debt is likely
why researchers in the survey of \citet{Nguyen-HoanEtAl2010} rate
maintainability as the third most important software quality. More recently the
push for sustainable software \citep{deSouzaEtAl2019} is motivated by the pain
that past developers have had with accumulating too much technical debt.

The most popular, with five out of nine interviewees mentioning it, strategy for
ensuring maintainability was to use a modular approach, with often repeated
functions in a library.  Other strategies that were mentioned for improving
maintainability include supporting third-party extensions, an easy-to-understand
architecture, a dedicated architect, starting from simple solutions, and
documentation.  The \textit{3D Slicer} team used a well-defined structure for
the software, which they named as an ``event-driven MVC pattern''. Moreover,
\textit{3D Slicer} discovers and loads necessary modules at runtime, according
to the configuration and installed extensions. The \textit{BioImage Suite Web}
team had designed and re-designed their software multiple times in the last 10+
years. They found that their modular approach effectively supports
maintainability \citep{Joshi2011}.

\item \textbf{Reproducibility:}  Interviewees stressed the importance of
documentation for both users and developers throughout the interviews. They
emphasize that a lack of time and funding (\ppref{P_LackDevTime}) has a negative
effect on the documentation. Most of the developers are scientific researchers
evaluated on the scientific papers that they produce. Writing and updating
documentation is something that is done in their free time, if that time arises.
Others also mention inadequate research software documentation
\citep{PintoEtAl2018, WieseEtAl2019}.  The problem also arises with non-research
software \citep{LethbridgeEtAl2003}. Recommendations on the development of
research software state that developers should critically evaluate their own
development processes in terms of quality assurance and comply with
international standards for software documentation
\citep{KaterbowAndFeulner2018}.

We discussed threats to reproducibility and strategies for improving it.  The
threats that were mentioned include closed-source software, no user interaction
tests, no unit tests, using different versions of some common libraries
\wss{because the interface and/or behaviour of the library could have changed?
Ask Ao} \ad{Yes. Behaviour change could be caused by a lib changing to use
different algorithms or different dependencies}, variability
between CPUs, and misinterpretation of how manufacturers
create medical images. The most commonly cited (by 6 teams) strategy to improve
reproducibility was testing (regression tests, unit tests, having good tests).
The second most common strategy (mentioned by 5 teams) is making code, data, and
documentation available, possibly by creating open-source libraries.  Other
ideas that were mentioned include running the same tests on all platforms, a
dockerized version of the software to insulate it from the OS environment, using
standard libraries, monitoring the upgrades of the library dependencies, clearly
documenting the version information, bringing along the exact versions of all
the dependencies with the software, providing checksums of the data, and
benchmarking the software against other software that overlaps in functionality.
Specifically one interviewee suggested using \textit{3D Slicer} as the benchmark
to test their reproducibility.

@@

@@

\item \textbf{Installability} (Section~\ref{sec_result_installability})
    \item providing clear instructions;
    \item automating installation;
    \item including all dependencies in the installer;
    \item avoiding heavily depending on other commercial products (e.g.\ Matlab);
    \item potentially building a web application that needs no installation.
\item \textbf{Correctness \& Verifiability}
(Section~\ref{sec_result_correctness_verifiability} and
Section~\ref{sec_interview_software_qualities})
    \item test-driven development with unit tests, integration tests, and
    nightly tests;
    \item two stage development process with stable release \& nightly builds;
    \item CI/CD;
    \item requirements specifications and theory manuals \citep{Smith2016, SmithAndLai2005}.
    \item static code analysis tools (e.g. Lint and SonarQube)
\item \textbf{Reliability} (Section~\ref{sec_result_reliability})
    \item test-driven development with unit tests, integration tests, and nightly tests.
    \item two stage development process with stable release \& nightly builds;
    \item descriptive error messages.
\item \textbf{Robustness} (Section~\ref{sec_result_robustness})
    \item designing with exception handling so the software can fail gracefully;
    \item descriptive error messages.
\item \textbf{Usability} (Section~\ref{sec_result_usability} and Section~\ref{sec_interview_software_qualities})
    \item usability tests and interviews with end users;
    \item adjusting according to users' feedbacks;
    \item getting started tutorials;
    \item user manuals;
    \item professional UX (User eXperience) designs;
    \item graphical user interface;
    \item active supports to users.
\item \textbf{Maintainability} (Section~\ref{sec_score_maintainability} and Section~\ref{sec_interview_software_qualities})
    \item use GitHub (or equivalent version control and project management environment);
    \item use a modular approach to design (we advocate basing the design on
    Parnas's principle of information hiding: ``system details that are likely
    to change independently should be the secrets of separate modules; the only
    assumptions that should appear in the interfaces between modules are those
    that are considered unlikely to change.'' \citep{ParnasEtAl2000})
    \item documentation for developers: project plan, developer’s manual, and API documentation.
\item \textbf{Reusability} (Section~\ref{sec_result_reusability})
    \item modular approach;
    \item API documentation;
    \item tools that generate software documentation for developers (e.g.\
    Doxygen, Javadoc, and Sphinx).
\item \textbf{Understandability} (Section~\ref{sec_result_understandability} and
Section~\ref{sec_interview_software_qualities})
    \item modular approach;
    \item good coding style: consistent indentation and formatting style;
    consistent, distinctive, and meaningful code identifiers; keeping parameters
    in the same order for all functions; avoiding hard-coded constants (other
    than 0 and 1);
    \item clear comments, indicating what is being done, not how;
    \item description of algorithms used;
    \item documentation of explicit requirements on coding standards;
    \item communication between developers and users via GitHub issues, mailing
    lists, and forums.
\item \textbf{Visibility/Transparency} (Section~\ref{sec_result_visibility_transparency})
    \item documents for the development process, contributor's guide, project
    status, development environment, and release notes.
\item \textbf{Reproducibility} (Section~\ref{sec_interview_software_qualities})
    \item test-driven development with unit tests, integration tests, and nightly tests.
    \item open-source;
    \item making data and documentation available;
    \item using open-source libraries.

\wss{Could ``reverse'' the list and list the recommendations and beside each the qualities 
that that recommendation helps with - this would reduce repetition.}

\subsection{Recommendations on Dealing With Limited Resources}
\label{sec_recommendations_limited_resources}

The limitation of resources has many faces, with the key manifestations being
lack of fundings, time, and developers. We summarized our discussion with the MI
software developers in Section~\ref{painpoints}.  Many of our recommendations
involve investing more effort into processes, tools and methods, so that the
limited resources can be used more effectively.  Our recommendations are as
follows:

\wss{Talk about increasing the number of developers.  CONTRIBUTING is rare
(Table~\ref{artifactspresent}), but it doesn't have to be.  Related to this
information for new developers is rare: Code Style Guide, Requirements, Design
Doc, API.}

\begin{itemize}
\item \textbf{Identify the root cause.} More fundings or developers may not
solve problems called by a lack of time. It is beneficial to identify the
underlying obstacles to the team.  \wss{Is there something from the mythical man
month that should be cited here?}

\item \textbf{Maintain good documentation.} Creating and updating documentation
consumes time, but can save much more time in the long term. If the users and
developers can find answers to their questions themselves, they are less likely
to abuse the team's issue tracker.  \wss{If it is an option, we could cite one
of our productivity related papers.}

\item \textbf{Adopt time-saving tools.} A good CI/CD tool (e.g.\ GitHub Actions)
saves time for building and deploying the product, and automated tests can work
in the background while developers are focusing on other tasks.

\item \textbf{Use test-driven development process.} Many people think writing
test cases is less rewarding than writing code, but without testing identifying
and fixing bugs can consume substantial resources. Setting up the test cases
costs time, but generates more benefits in the long run.

\item \textbf{Consider supporting third-party plugins or extensions.} Why not
let users share the burden? No software product can deliver every user's needs,
and the large quantity of features leads to more bugs and maintenance problems.
So it may be a good idea to shift some development and maintenance
responsibilities to the users. The users may also be happy with the extra
flexibility.

\item \textbf{Consider ``hibernating'' for a while.} When there aren't enough
developers, the team can shift from development mode toward maintenance mode.
The team can stop building new features for a while and instead fix bugs and
design problems from the past. If the development team can repay some of its
technical debt \citep{KruchtenEtAl2012}, the software qualities will likely
improve as a result.

\item \textbf{Commercialization is not always toxic.} Licensing the software to
commercial companies to use as internal modules of their products may bring
financial support to the team. Meanwhile, the project can stay open-source for
the community.
\end{itemize}

@@

\item \textbf{Maintain good documentation.} No matter what tech stack a team
uses, a well-maintained project plan, developer's manual, and API documentation
generally help team members to contribute more and make fewer mistakes.
\end{itemize}

>>>>

We based our interviews on a list of 20 questions, which can be found in
\citet{SmithEtAl2021}. Some questions are about the background of the software,
the development teams, the interviewees, and how they organize the projects. We
also ask about the developer's understandings of the users. Some questions focus
on the current and past difficulties, and the solutions the team has found, or
will try. We also discuss the importance and current situations of
documentation. A few questions are about specific software qualities, such as
maintainability, understandability, usability, and reproducibility. The
interviews are semi-structured based on the question list; we ask follow-up
questions when necessary.  The interview process presented here was approved by
the McMaster University Research Ethics Board under the application number 
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/MACREM/Application.pdf}
{MREB\#: 5219}.

@@

We identified the use of unit testing in less than half of the 29 projects. On
the other hand, the interviewees believed that testing (including usability
tests with users) was the top solution to improve correctness, usability, and
reproducibility.  This level of testing matches what was observed for LBM
software \citep{Michalski2021} and is apparently greater than the level of
testing for ocean modelling software.  \citet{JungEtAl2022} reports that ocean
modellers underemphasize testing.

As the observed artifacts in Table~\ref{artifactspresent} show, none of the 29
projects emphasize documentation. None of them had theory manuals, although we
did identify a road map in the \textit{3D Slicer} project.  We did not find
requirements specifications. Table~\ref{tab_opinion_doc} summarizes
interviewees' opinions on documentation. Interviewees from each of the eight
projects thought that documentation was essential to their projects, and most of
them said that it could save their time to answer questions from users and
developers. Most of them saw the need to improve their documentation, and only
three of them thought that their documentations conveyed information clearly
enough. Nearly half of developers also believed that the lack of time prevented
them from improving documentation.

@@

As Table~\ref{Tbl_Guidelines} suggests, an emphasis on documentation, especially
for new developers, is echoed in research software guidelines. Multiple
guidelines recommend a document explaining how to contribute to a project, often
named CONTRIBUTING. Guidelines also recommend tutorials, user guides and quick
start examples. \citet{SmithAndRoscoe2018} suggests including instructions
specifically for on-boarding new developers. For open source software in general
(not just research software), \citet{Fogel2005} recommends providing tutorial
style examples, developer guidelines, demos, and screenshots.

@@

Our interviews identified pain points related to a lack of time and funding,
technology hurdles, improving correctness, and improving usability.  In this
section, we go through each pain point and contrast the MI experience with
observations from other domains.  We also cover potential ways to address the
pain points, as promoted by the community.  (Later, in
Section~\ref{ch_recommendations}, we propose additional pain mitigation
strategies based on our experience.)  In addition to pain points, we summarize
MI developer strategies for improving maintainability and reproducibility.
Although the interviewees did not explicitly identify these two qualities as
pain points, they were discussed as part of our interview process
\citep{SmithEtAl2021}.  The interviewee's practices for addressing pain points
and improving quality can potentially be emulated by other MI developers.
Moreover, these practices may provide examples that can be followed by other
research software domains.

\wss{CHECK  THESE, after writing all the PPs} \citet{PintoEtAl2018} lists some pain
points that did not come up in our conversations with MI developers:
Cross-platform compatibility, interruptions while coding, scope bloat, lack of
user feedback, hard to collaborate on software projects, and aloneness.
\citet{WieseEtAl2019} repeat some previous pain points and add the following:
dependency management, data handling concerns (like data quality, data
management and data privacy) \wss{Actually mentioned by MI software},
reproducibility, and software scope determination. Although MI developers did
not mention these pain points, we cannot conclude that they are not relevant for
MI software development, since we only interviewed nine developers for about
an hour each.

@@

\begin{itemize}
\item Shifting from development to maintenance when the team does not have
enough developers for building new features and fixing bugs at the same time;
\item Improving documentation to save time answering users' and developers'
questions;
\item Supporting third-party plugins and extensions; and,
\item Using GitHub Actions for continuous integration and continuous
development.
\end{itemize}

\item[P\refstepcounter{pnum}\thepnum \label{P_LackFunding}:] \textbf{Lack of
Funding:} Developers felt the pain of having to attract funding to develop and
maintain their software. For instance, the interviewees from \textit{3D Slicer}
and \textit{OHIF} said getting funding for software maintenance is more
challenging than finding funding for research. The interviewee from the
\textit{ITK-SNAP} team thought more funding was a way to solve the lack of time
problem, because they could hire more dedicated developers. On the other hand,
the interviewee from the \textit{Weasis} team did not feel that funding could
solve the same problem, since they would still need time to supervise the project.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_TechnologyHurdles}:]
\textbf{Technology Hurdles:} The technology hurdles mentioned by MI developers
include: hard to keep up with changes in OS and libraries, difficult to transfer
to new technologies, hard to support multiple OSes, and hard to support lower-end
computers. Developers expressed difficulty balancing between four factors:
cross-platform compatibility, convenience to development and maintenance,
performance, and security.

@@

\begin{itemize}
\item Adopting a web-based approach with backend servers, to better support
lower-end computers;
\item Using memory-mapped files to consume less computer memory, to better
support lower-end computers; 
\item Using computing power from the computers GPU for web applications;
%\item Increasing funding;
\item Maintaining better documentations to ease the development and maintenance
processes;
\item Improving performance via more powerful computers, which one interviewee
pointed out has already happened to reduce the balance problem.
\end{itemize}

As the above list shows, developers perceive that web-based applications will
address the technology hurdle.  Table~\ref{tab_native_vs_web} shows the teams'
choices between native application and web application. Most of the 29 teams (24
of 29, or 83\%) chose to develop native applications. For the eight teams we
interviewed, three of them were building web applications, and the
\textit{MRIcroGL} team was considering a web-based solution.

@@

As implied by the above threats to correctness, testing was the most often
mentioned strategy for MI developers for ensuring correctness.  Seven teams
mentioned test related activities, including test-driven development, component
tests, integration tests, smoke tests, regression tests, self tests and
automated tests.  With the common emphasis on testing to improve correctness, MI
software is ahead of some other scientific domains.  For scientific software in
general \citet{PintoEtAl2018} mention the problem of insufficient testing and
\citet{HannayEtAl2009} show that more developers think testing is important than
the number that believe they have a sufficient understanding of testing
concepts.  Our study of LBM software suggests that this domain shares the
challenges of insufficient testing and insufficient understanding of testing
concepts \citep{SmithEtAl2022}. Automated testing is a specific challenge for
LBM software since free testing services do not offer adequate facilities for
large amounts of data \citep{SmithEtAl2022}. Although not specifically mentioned
during our interviews, the large data sets for MI likely cause a challenge for
using free testing services, like GitHub Actions.

Research software in general often struggles with the oracle problem for testing
because for many potential test cases the developer doesn't have a means to
judge the correctness of their calculated solutions \citep{HannayEtAl2009,
KanewalaAndBieman2013, KellyEtAl2011, WieseEtAl2019}.  The MI developers did not
allude to this challenge, likely because for a give image (test case) it is
possible to determine, possibly using other software, the expected analysis
results.

A frequently cited strategy for building confidence in correctness (mentioned by
3 interviewees) is a two state development process with stable releases and
nightly builds.  Other strategies for ensuring correctness that came up during
the interviews include CI/CD, using de-identified copies of medical images for
debugging, sending beta versions to medical workers who can access the data to
do the tests, and collecting/maintaining a dataset of problematic images.  Some
additional strategies used by MI developers include:

\begin{itemize}
\item Using open datasets, like the datasets for the liver \citep{BilicEtAl2019}
and brain \citep{MenzeEtAl2015} tumor segmentation benchmarks.
\item If (part of) the team belongs to a medical school or a hospital, using the
datasets they can access;
\item If the team has access to MRI scanners, self-building sample images for
testing;
\item If the team has connections with MI equipment manufacturers, asking for
their help on data format problems;
\end{itemize}

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_Usability}:]
\textbf{Usability:}

The discussion with the developers focused on usability issues for two classes
of users: the end users and other developers.  The threats to usability for end
users include an unintuitive user interface, inadequate feedback from the
interface (such as lack of a progress bar), users being unable to determine the purpose of
the software, not all users knowing if the software includes certain features, not
all users understanding how to use the command line tool, and not all users
understanding that the software is a web application. For developers the threats to
usability include not being able to find clear instructions on how to deploy the
software, and the architecture being difficult for new developers to understand.

At least to some extent the problems for MI software users are due to holes in
their background knowledge.  The survey of \citet{WieseEtAl2019} for research
software in general also mentioned that users do not always have the expertise
required to install or use the software. \citet{SmithEtAl2022} observes a
similar pattern for LBM software, with several LBM developers noting that users
sometimes try to use incorrect method combinations. Furthermore, some LBM users
think that the packages will work out of the box to solve their cases, while in
reality CFD knowledge needs to be applied to correctly modify the packages for a
new endeavour.

To improve the usability of MI software, the most common strategies mentioned by
developers are as follows:

\begin{itemize}[i)]
    \item use documentation (user manuals, mailing lists, forums) (mentioned by
    4 developers)
    \item usability tests and interviews with end users; and, (mentioned by 3
    developers)
    \item adjusting the software according to user feedback. (mentioned by 3
    developers)
\end{itemize}

Other suggested and practiced strategies include a graphical user interface,
testing every release with active users, making simple things simple and
complicated things possible, focusing on limited number of functions, icons with
clear visual expressions, designing the software to be intuitive, having a UX
designer, dialog windows for important notifications, providing an example for
users to follow, downsampling images to consume less memory, and an option to
load only part of the data to boost performance.  The last two points recognize
that an important component of usability is performance, since poor performance
frustrates users.

@@

Up to this point, we have covered the pain points that came up in interviews
with MI developers, along with a summary of the techniques that are currently
used to address these pain points.  Although the developers did not explicitly
identify the qualities of maintainability and reproducibility as pain points in
our interviews, as part of our interview questions
(Section~\ref{sec_interview_methods}) they did share their approaches for
improving these qualities, as discussed below.

\begin{enumerate}
\item \textbf{Maintainability:} Although not explicitly highlighted as a pain
point during our interviews, \citet{Nguyen-HoanEtAl2010} rate maintainability as
the third most important software quality for research software in general. The push for
sustainable software \citep{deSouzaEtAl2019} is motivated by the pain that past
developers have had with accumulating too much technical debt
\citep{KruchtenEtAl2012}.  For LBM software, \citet{SmithEtAl2022} identifies
technical debt as one of the developer pain points.

To improve maintainability, the most popular (with five out of nine interviewees
mentioning it) strategy is to use a modular approach, with often repeated
functions in a library.  Other strategies that were mentioned for improving
maintainability include supporting third-party extensions, an easy-to-understand
architecture, a dedicated architect, starting from simple solutions, and
documentation.  The \textit{3D Slicer} team used a well-defined structure for
the software, which they named as an ``event-driven MVC pattern''. Moreover,
\textit{3D Slicer} discovers and loads necessary modules at runtime, according
to the configuration and installed extensions. The \textit{BioImage Suite Web}
team had designed and re-designed their software multiple times in the last 10+
years. They found that their modular approach effectively supports
maintainability \citep{Joshi2011}.

\item \textbf{Reproducibility:}  Although the MI developers did not mention
reproducibility explicitly as a pain point, they did mention the need to improve
documentation.  Good documentation doesn't just address the pain points of lack
of developer time (\ppref{P_LackDevTime}), technology hurdles
(\ppref{P_TechnologyHurdles}), usability \ppref{P_Usability}, and
Maintainability.  Documentation is also necessary for reproducibility. The
challenges of inadequate documentation are a known problem for research software
\citep{PintoEtAl2018, WieseEtAl2019} and for non-research software
\citep{LethbridgeEtAl2003}.

In our interviews, we discussed threats to reproducibility and strategies for
improving it.  The threats that were mentioned include closed-source software,
no user interaction tests, no unit tests, the need to change versions of some
common libraries, variability between CPUs, and misinterpretation of how
manufacturers create medical images.

The most commonly cited (by 6 teams) strategy to improve reproducibility was
testing (regression tests, unit tests, having good tests). The second most
common strategy (mentioned by 5 teams) is making code, data, and documentation
available, possibly by creating open-source libraries.  Other ideas that were
mentioned include running the same tests on all platforms, a dockerized version
of the software to insulate it from the OS environment, using standard
libraries, monitoring the upgrades of the library dependencies, clearly
documenting the version information, bringing along the exact versions of all
the dependencies with the software, providing checksums of the data, and
benchmarking the software against other software that overlaps in functionality.
Specifically one interviewee suggested using \textit{3D Slicer} as the benchmark
to test their reproducibility.

@@

- not repeating best practices mentioned previously, like CI/CD, version
control, testing, etc.

@@

@@
